Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-24 paper/section-instantiations.tex
small changes
iso

We can generalise this isomorphism to type
of the form $\forall t\mathord:\SynTransl{2}.\tyPrim{vec}{e,t}\to A$
in which $A$ contains no quantifiers. 
To be precise, we have the following isomorphism:
\[
\Delta\vdash(\forall t\mathord:\SynTransl{2}.\tyPrim{vec}{e,t}\to A)
\cong A[0/t]
\]
where $A[0/t]$ denotes substitution of the identity translation $0$
for index variable $t$ in type $A$. This isomorphism formalises the
equivalence between \emph{coordinate-free} geometry, expressed by a
polymorphic type whose first argument can be thought of as the
\emph{origin} with respect to which $A$ is specified, and a
\emph{coordinate-based} geometry, expressed by the type $A[0/t]$, in
which the origin is fixed at $(0,0)$. It is sometimes said that an
affine space is a vector space that has forgotten its origin; we have
captured this in a type isomorphism.

>>>>

We can generalise this isomorphism substantially, proving
that for any quantifier-free type $A$, 
the type $\forall t\mathord:\SynTransl{2}.\tyPrim{vec}{e,t}\to A$
is isomorphic to $A[0/t]$, where $A[0/t]$ 
denotes substitution of the identity translation $0$
for index variable $t$ in type $A$. This isomorphism formalises the
equivalence between \emph{coordinate-free} geometry, expressed by a
polymorphic type whose first argument can be thought of as the
\emph{origin} with respect to which $A$ is specified, and a
\emph{coordinate-based} geometry, expressed by the type $A[0/t]$, in
which the origin is fixed at $(0,0)$. It is sometimes said that an
affine space is a vector space that has forgotten its origin; we have
captured this in a type isomorphism.
